---
title: "Advanced functions for package developers and contributors"
date: "Last updated `r Sys.Date()`"
output: 
    rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

## Clone or download packages

The `clone_package` function copies a Data Package from one DataOne member node to another. It can also be used to copy an older version of a Data Package to the same member node in order to restore it, provided that the old Package is then obsoleted by the copied version.

NOTE: BUGS ARE CURRENTLY BEING FIXED

Example:

```{r}
cn_pull <- CNode("PROD")
mn_pull <- getMNode(cn_pull, "urn:node:ARCTIC")
cn_push <- CNode('STAGING')
mn_push <- getMNode(cn_push,'urn:node:mnTestARCTIC')
clone_package(mn_pull, mn_push, "resource_map_doi:10.18739/A2RZ6X")
```

## Create a dummy package

The function `create_dummy_package2` creates a fuller package than create_dummy_package but is otherwise based on the same concept. This dummy package includes multiple data objects (2 csv's, and 2 jpg's), responsible parties, geographic locations, method steps, etc. You can also define a unique title for the package to distinguish it from other test packages.

```{r}
create_dummy_package2(mn, title = "A Dummy Package")
```

## Get NSF awards

The `get_awards` function uses the NSF API to get all records pertaining to the Arctic or Polar programs.

Example:

```{r}
all_awards <- get_awards()
new_awards <- get_awards(from_date = "01/01/2017")
```

## Which in EML

The `which_in_eml` function returns indices within an EML list that contain an instance where test == TRUE. See examples for more information.

```{r}
# Question: Which creators have a surName "Smith"?
n <- which_in_eml(eml@dataset@creator, "surName", "Smith")
# Answer: eml@dataset@creator[n]

# Question: Which dataTables have an entityName that begins with "2016"
n <- which_in_eml(eml@dataset@dataTable, "entityName", function(x) {grepl("^2016", x)})
# Answer: eml@dataset@dataTable[n]

# Question: Which attributes in dataTable[[1]] have a numberType "natural"?
n <- which_in_eml(eml@dataset@dataTable[[1]]@attributeList@attribute, "numberType", "natural")
# Answer: eml@dataset@dataTable[[1]]@attributeList@attribute[n]

# Question: Which dataTables have at least one attribute with a numberType "natural"?
n <- which_in_eml(eml@dataset@dataTable, "numberType", function(x) {"natural" %in% x})
# Answer: eml@dataset@dataTable[n]
```

