---
title: "Functions for PIs"
date: "Last updated `r Sys.Date()`"
output: 
    rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Functions for PIs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```


## Download package

The `download_package()` function downloads all of the data objects in a data package to the local filesystem. It is particularly useful when a data package is too large to download using the web interface.

Setting `check_download_size` to `TRUE` is recommended if you are uncertain of the total download size and want to avoid downloading very large data packages.

This function will also download any data objects it finds in any child data packages of the input data package. If you would only like to download data from one data package, set `download_child_packages` to `FALSE`.

Example:

```{r}
cn <- CNode("PROD")
mn <- getMNode(cn, "urn:node:ARCTIC")

download_package(mn, "resource_map_urn:uuid:2b4e4174-4e4b-4a46-8ab0-cc032eda8269")
```
